Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2022-04-16 doc/manuscript/ESSDmanuscript.Rmd
rearrangement - switch sections 3 & 4

# Mapping ForC to EFDB

The majority of information required by EFDB was present in previous versions of ForC [].
We made modest structural changes to ForC (Table ##) to allow complete records to be restructured for automated population of EFDB data entry forms using R ().

## Carbon cycle variables

## Land use categories

@@

To support export of data to EFDB, and to improve the overall quality of the ForC database, we defined ## new variables, implemented some modest restructuring, resolved duplicate records, and conducted quality control.
This section describes changes relative to ForC v2.0 [@anderson-teixeira_forc_2018].

@@

- Data location within source - Because EFDB will not accept data which has been digitized (from graphs) while ForC does, it was necessary to review and note the location of the data within the original source

@@

library(knitr)
library(kableExtra)
knitr::kable(C_variables_table, format = "latex",
             longtable = TRUE,
             caption = "\\textbf{Numbers of records of ForC variables relevant to, and sent to, EFDB.} Relationships of variables to IPCC-defined forest C pools (Table 1) and to each other are illustrated in Figure 1. ") %>%
  kableExtra::kable_styling(full_width = TRUE) %>%
  row_spec(0, bold = TRUE)  %>%
  row_spec(1, bold = TRUE)  %>% #biomass
  row_spec(6, bold = TRUE)  %>% #agb
  row_spec(14, bold = TRUE) %>% #root
  row_spec(25, bold = TRUE)  %>% #dead wood
  row_spec(33, bold = TRUE)  %>% #litter
  row_spec(40, bold = TRUE)  %>% #som
  row_spec(44, bold = TRUE)  #total

```

>>>>

@@

Previous versions of ForC [@refs] contained most of the information required for transfer to EFDB, and, more broadly, to inform C accounting under IPCC guidelines. 
However, modest changes to the structure and contents of ForC were needed in order to provide all information fequired by EFDB and to improve ForC's capacity to serve as a repository of valuable information for forest C accounting under IPCC guidelines.
To support export of data to EFDB, and to improve the overall quality of the ForC database, we added ## new fields, defined ## new variables, implemented some modest restructuring (Table ##), resolved duplicate records, and conducted quality control.
This section describes changes relative to ForC v2.0 [@anderson-teixeira_forc_2018].

## Adding new fields

@@

*Data location within source*-  Because EFDB will not accept data which has been digitized (from graphs) while ForC does, it was necessary to review and note the location of the data within the original source

# ForC to EFDB data transfer

To transfer data from ForC into the EFDB, we populated EFDB's bulk import form ("EFDB bulk import.xlsx"), using R scripts to restructure complete, reviewed records for entry into this form.

## Mapping ForC to EFDB
### Carbon cycle variables

### Land use categories

## Review and posting of data

@@

library(knitr)
library(kableExtra)
knitr::kable(C_variables_table, format = "latex",
             longtable = TRUE,
             caption = "\\textbf{Numbers of records of ForC variables relevant to, and sent to, EFDB.} Relationships of variables to IPCC-defined forest C pools (Table 1) and to each other are illustrated in Figure 1. ") %>%
  kableExtra::kable_styling(full_width = TRUE) %>%
  row_spec(0, bold = TRUE)  %>%
  row_spec(1, bold = TRUE)  %>% #biomass
  row_spec(6, bold = TRUE)  %>% #agb
  row_spec(14, bold = TRUE) %>% #root
  row_spec(25, bold = TRUE)  %>% #dead wood
  row_spec(33, bold = TRUE)  %>% #litter
  row_spec(40, bold = TRUE)  %>% #som
  row_spec(44, bold = TRUE)  #total
```

### 2022-04-16 doc/manuscript/ESSDmanuscript.tex
rearrangement - switch sections 3 & 4

\section{Mapping ForC to EFDB}

The majority of information required by EFDB was present in previous
versions of ForC {[}{]}. We made modest structural changes to ForC
(Table \#\#) to allow complete records to be restructured for automated
population of EFDB data entry forms using R ().

\subsection{Carbon cycle variables}

@@

To support export of data to EFDB, and to improve the overall quality of
the ForC database, we defined \#\# new variables, implemented some
modest restructuring, resolved duplicate records, and conducted quality
control. This section describes changes relative to ForC v2.0
\citep{anderson-teixeira_forc_2018}.

@@

\begin{itemize}
\tightlist
\item
  Data location within source - Because EFDB will not accept data which
  has been digitized (from graphs) while ForC does, it was necessary to
  review and note the location of the data within the original source
\end{itemize}

@@

As of April 15, 2022, ForC (v4.0) contained NA independent records (NA
total), NA of which were for variables relevant to EFDB (Fig. 1). These
records were distributed across all forested continents and ecozones,
with particularly high concentrations in \emph{{[}ecozone(s){]}} and low
concentrations in \emph{{[}ecozone(s){]}} (Fig. 2). The most widely
represented forest type was \emph{{[}type{]}}, followed by
\emph{{[}type{]}} and \emph{{[}type{]}} (Fig. 3).

@@

As of April 15, 2022, we had reviewed and sent NA, NA of which have been
reviewed, accepted, and posted (Fig. 2-3, Table 2). \emph{{[}DETAILS{]}}

>>>>

@@

Previous versions of ForC \citep{refs} contained most of the information
required for transfer to EFDB, and, more broadly, to inform C accounting
under IPCC guidelines. However, modest changes to the structure and
contents of ForC were needed in order to provide all information
fequired by EFDB and to improve ForC's capacity to serve as a repository
of valuable information for forest C accounting under IPCC guidelines.
To support export of data to EFDB, and to improve the overall quality of
the ForC database, we added \#\# new fields, defined \#\# new variables,
implemented some modest restructuring (Table \#\#), resolved duplicate
records, and conducted quality control. This section describes changes
relative to ForC v2.0 \citep{anderson-teixeira_forc_2018}.

\subsection{Adding new fields}

@@

\emph{Data location within source}- Because EFDB will not accept data
which has been digitized (from graphs) while ForC does, it was necessary
to review and note the location of the data within the original source

\section{ForC to EFDB data transfer}

To transfer data from ForC into the EFDB, we populated EFDB's bulk
import form (``EFDB bulk import.xlsx''), using R scripts to restructure
complete, reviewed records for entry into this form.

\subsection{Mapping ForC to EFDB}

\subsubsection{Carbon cycle variables}

\subsubsection{Land use categories}

\subsection{Review and posting of data}

@@

As of April 16, 2022, ForC (v4.0) contained NA independent records (NA
total), NA of which were for variables relevant to EFDB (Fig. 1). These
records were distributed across all forested continents and ecozones,
with particularly high concentrations in \emph{{[}ecozone(s){]}} and low
concentrations in \emph{{[}ecozone(s){]}} (Fig. 2). The most widely
represented forest type was \emph{{[}type{]}}, followed by
\emph{{[}type{]}} and \emph{{[}type{]}} (Fig. 3).

@@

As of April 16, 2022, we had reviewed and sent NA, NA of which have been
reviewed, accepted, and posted (Fig. 2-3, Table 2). \emph{{[}DETAILS{]}}
